---
title: "Monkey deep analysis:distribution test"
author: "yejg"
date: "2018/2/1"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE,tidy = TRUE,fig.width=12, fig.height=10,highlight = TRUE)
```

### Load the packages
```{r}
library(Seurat)
library(data.table)
library(NMF)
library(rsvd)
library(Rtsne)
library(ggplot2)
library(cowplot)
library(sva)
library(igraph)
library(cccd)
library(KernSmooth)
library(beeswarm)
library(stringr)
library(formatR)
source('../tools.R')
library(DESeq2)
```
## Step 1: All data: Analysis based on sample group
###  Read data
###  Data QA
```{r}
monkey.only.pro<-Load_data(data_dir = '../data/monkey.txt')
rownames(monkey.only.pro)<-unlist(lapply(rownames(monkey.only.pro),str_to_upper))
important.genes<-c('ITGB4','ABCB5','KRT19','ACTB','KRT12','KRT5',
                   'GAPDH','KRT3','PAX6','WNT7A','KRT14','TRP63','KRT10')
table(unlist(lapply(colnames(monkey.only.pro),
                    function(x)return(str_split(x,'_')[[1]][2]))))
table(unlist(lapply(colnames(monkey.only.pro),
                    function(x)return(str_split(x,'_')[[1]][1]))))
```

###  Create Seurat object and not caculate DESeq,but set **min.cells=10** and **min.genes=2** 
```{r}
# only select the cells contain 10 genes expressed at least,select the genes must be expressed in two cells at least
monkey.all.pbmc<-DESeq_SeuratObj(X=monkey.only.pro,DESq = FALSE,min.cells = 10,min.genes = 2)
all.sample.group<-unlist(lapply(monkey.all.pbmc@cell.names,function(x)return(str_split(x,'_')[[1]][1])))
all.sample.size<-unlist(lapply(monkey.all.pbmc@cell.names,function(x)return(str_split(x,'_')[[1]][2])))
#  reset ident
monkey.all.pbmc<-SetIdent(monkey.all.pbmc,cells.use = monkey.all.pbmc@cell.names,ident.use = all.sample.size)
table(all.sample.group,all.sample.size)
```

##  Dimensionality reduction
###  **PCA** and **tSNE**
    Here,do the dimensionality reduction using the PCA, tSNE method 
```{r}
all.pbmc<-PCA.TSNE(object = monkey.all.pbmc,pcs.compute =FALSE,num.pcs = 28)
```

```{r}
DimPlot(all.pbmc,reduction.use = 'tsne',pt.size = 4)  
DimPlot(all.pbmc,reduction.use = 'pca',pt.size = 4)  
```


###  In the sample cell size,compare the sample distribution
```{r}
pca<-data.frame(all.pbmc@dr$pca@cell.embeddings)
tsne<-data.frame(all.pbmc@dr$tsne@cell.embeddings)
pca$cell.size<-all.sample.size
pca$cell.group<-all.sample.group
tsne$cell.size<-all.sample.size
tsne$cell.group<-all.sample.group
```
####  PCA method
```{r}
ggplot(data=pca)+geom_point(aes(x=PC1,y=PC2),color='red')+
  geom_density2d(aes(x=PC1,y=PC2),contour=TRUE)+
  facet_wrap(~cell.size+cell.group)
```

#### tSNE method
```{r}
ggplot(data=tsne)+geom_point(aes(x=tSNE_1,y=tSNE_2),color='red')+
  geom_density2d(aes(x=tSNE_1,y=tSNE_2),contour=TRUE)+facet_wrap(~cell.size+cell.group)
```

####  density method
```{r}
monkey.lognorm<-data.frame(FetchData(all.pbmc,vars.all =all.pbmc@var.genes))
monkey.lognorm$cell.size<-all.sample.size
monkey.lognorm$cell.group<-all.sample.group
monkey.lognorm.melt<-melt(monkey.lognorm)
```

```{r}
ggplot(data = monkey.lognorm.melt,aes(x=value))+
  geom_density(kernel='gaussian',fill='red')+scale_y_sqrt()+scale_x_sqrt()+facet_wrap(~cell.size+cell.group)
```

## Distribution test
####  the Kolmogorov–Smirnov test (K–S test or KS test) is a nonparametric test of the equality of continuous, one-dimensional probability distributions that can be used to compare a sample with a reference probability distribution (one-sample K–S test), or to compare two samples (two-sample K–S test)

##### The null distribution of this statistic is calculated under the null hypothesis that the sample is drawn from the reference distribution (in the one-sample case) or that the samples are drawn from the same distribution (in the two-sample case). In each case, the distributions considered under the null hypothesis are continuous distributions but are otherwise unrestricted
```{r}
size.group.table<-as.data.frame(as.matrix(table(all.sample.group,all.sample.size)))
size.group.table<-size.group.table[size.group.table$Freq>0,]  # only test cell size,group both not null
```
###  6um:under the cell size 6um test
```{r}
KS.test.comb(all.pbmc,genes = important.genes,cell_size = '6um')
```

###  10um:under the cell size 10um test
```{r}
KS.test.comb(all.pbmc,genes = important.genes,cell_size = '10um')
```
     
     
###  20um:under the cell size 20um test
```{r}
KS.test.comb(all.pbmc,genes = important.genes,cell_size = '20um')
```

