---
title: "Monkey summary analysis"
author: "yejg"
date: "2018/1/26"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE,tidy = TRUE,fig.width=12, fig.height=10,highlight = TRUE)
```

### Load the packages
```{r}
library(Seurat)
library(data.table)
library(NMF)
library(rsvd)
library(Rtsne)
library(ggplot2)
library(cowplot)
library(sva)
library(igraph)
library(cccd)
library(KernSmooth)
library(beeswarm)
library(stringr)
library(formatR)
source('../tools.R')
library(DESeq2)
```

## Step 1: All data: Analysis based on sample group
###  Read data
###  Data QA
```{r}
monkey.only.pro<-Load_data(data_dir = '../data/monkey.txt')
important.genes<-c('ITGB4','ABCB5','KRT19','ACTB','KRT12','KRT5',
                   'GAPDH','KRT3','PAX6','WNT7A','KRT14','TP63','KRT10')

table(unlist(lapply(colnames(monkey.only.pro),
                    function(x)return(str_split(x,'_')[[1]][2]))))
table(unlist(lapply(colnames(monkey.only.pro),
                    function(x)return(str_split(x,'_')[[1]][1]))))
```
###  Create Seurat object and not caculate DESeq,but set **min.cells=10** and **min.genes=2** 
```{r}
# only select the cells contain 10 genes expressed at least,select the genes must be expressed in two cells at least
monkey.all.pbmc<-DESeq_SeuratObj(X=monkey.only.pro,DESq = FALSE,min.cells = 10,min.genes = 2)
all.sample.group<-unlist(lapply(monkey.all.pbmc@cell.names,function(x)return(str_split(x,'_')[[1]][1])))
all.sample.size<-unlist(lapply(monkey.all.pbmc@cell.names,function(x)return(str_split(x,'_')[[1]][2])))
```
## Figure Explore
###  First,use the plot,eg. Barplot,density...,we can explore some message from sample

```{r}
monkey.imp.lognorm<-data.frame(FetchData(monkey.all.pbmc,vars.all = important.genes[important.genes%in%rownames(monkey.all.pbmc@raw.data)]))
monkey.imp.lognorm$cell.size<-unlist(lapply(rownames(monkey.imp.lognorm),function(x)return(str_split(x,'_')[[1]][2])))
monkey.imp.lognorm$cell.sample<-unlist(lapply(rownames(monkey.imp.lognorm),function(x)return(str_split(x,'_')[[1]][1])))
monkey.imp.lognorm.melt<-melt(monkey.imp.lognorm)
```

#### Boxplot
```{r}
p<-ggplot(data = monkey.imp.lognorm.melt,aes(y=value,x=cell.sample,fill=cell.sample))
p+geom_boxplot()+guides(fill=guide_legend(title="Cell Sample"))+facet_wrap(~variable)
```

#### Density,histogram
```{r}
ggplot(data = monkey.imp.lognorm.melt,aes(x=value,fill=variable))+
  geom_density(kernel='gaussian')+scale_x_sqrt()+
  facet_wrap(~cell.sample)


ggplot(data = monkey.imp.lognorm.melt,aes(x=value,fill=variable))+
  geom_density(kernel='gaussian',position = 'stack')+scale_x_sqrt()+facet_wrap(~cell.sample)

ggplot(data = monkey.imp.lognorm.melt,aes(x=value,fill=variable))+
   geom_histogram()+scale_x_sqrt()+facet_wrap(~cell.sample)

```


```{r}
Group_Bar(monkey.all.pbmc@raw.data,group = all.sample.group)
Group_Bar(monkey.all.pbmc@raw.data,group = all.sample.size)

# We are interested in the gene ITGB4 
GenePlot(monkey.all.pbmc,gene1 = 'ITGB4',gene2 =important.genes[3])

VlnPlot(monkey.all.pbmc,features.plot = important.genes[important.genes%in%rownames(monkey.all.pbmc@raw.data)],y.lab.rot = 90)  # Violinn plot of gene ITGB in all sample
```
##  Dimensionality reduction
###  **PCA** and **tSNE**
    Here,do the dimensionality reduction using the PCA, tSNE method 
```{r}
all.pbmc<-PCA.TSNE(object = monkey.all.pbmc,pcs.compute =FALSE,num.pcs = 28)
```



### After the PCA and tSNE,try plot: Featureplot of **ITGB4**,four var.genes,PCA plot,tSNE plot...
```{r}
# FeaturePlot(object = all.pbmc,features.plot ='ITGB4',pt.size = 4,no.legend = FALSE)  # ITGB4 gene in part dataset
FeaturePlot(object = all.pbmc,features.plot=
              important.genes[important.genes%in%rownames(all.pbmc@raw.data)],
            pt.size = 1,no.legend = FALSE,
            reduction.use = 'pca')  

FeaturePlot(object = all.pbmc,features.plot=
              important.genes[important.genes%in%rownames(all.pbmc@raw.data)],
            pt.size = 1,no.legend = FALSE,
            reduction.use = 'tsne') 

DimPlot(all.pbmc,reduction.use = 'tsne',pt.size = 4)  #  grour by sample
DimPlot(all.pbmc,reduction.use = 'pca',pt.size = 4)  #  grour by sample
DimHeatmap(all.pbmc,reduction.type = 'pca',check.plot = FALSE)


FeatureHeatmap(all.pbmc,features.plot = 'ITGB4',pt.size = 3,plot.horiz = TRUE,
               cols.use = c("lightgrey", "blue"))
```


### Heatmap for important genes
```{r}
monkey.heatmap<-Heatmap_fun(genes                     =important.genes[important.genes%in%rownames(all.pbmc@raw.data)],
                           tpm.data = all.pbmc@scale.data,
                           condition = unique(as.character(all.pbmc@ident)),
                           all.condition = as.character(all.pbmc@ident))

NMF::aheatmap(monkey.heatmap[[2]], Rowv = NA, Colv = NA, annCol = monkey.heatmap[[1]], 
              scale = "none")

```

The heatmap of genes `r important.genes[important.genes%in%rownames(all.pbmc@raw.data)]` .It tells us that **KRT14,WN&7A,ITGB4** expressed differently across sample,expressed more significant.


###  Next,Spectral k-means clustering on single cells based on PCA
```{r}
all.pbmc<-KClustDimension(all.pbmc,reduction.use = 'pca',k.use =length(unique(all.sample.group)))
clusters.pca<-all.pbmc@meta.data$kdimension.ident
DimPlot(all.pbmc,pt.size = 4,group.by ='kdimension.ident')
```

### Spectral k-means clustering on single cells based on tSNE
```{r}
all.pbmc<-KClustDimension(all.pbmc,reduction.use = 'tsne',k.use =length(unique(all.sample.group)))
clusters.tsne<-all.pbmc@meta.data$kdimension.ident
DimPlot(all.pbmc,pt.size = 4,group.by ='kdimension.ident',reduction.use = 'tsne')
```


##  Differential expression
    Next,we will have analysis on gene differential expression.Find maker genes across sample.We use the method: **wilcox test**
```{r}
#  Finds markers (differentially expressed genes) for each of the identity classes in a dataset
monkey.markers<-FindAllMarkers(all.pbmc,test.use = 'bimod',print.bar = FALSE)
head(monkey.markers)
```

We check whether the important genes are still in the marker genes we found from the DESeq analysis.
the genes:`r important.genes[important.genes%in%monkey.markers$gene]` are still in the marker genes.  


### Bar plot of gene's p.val
```{r,echo=FALSE}
genes.monkey.dp<-monkey.markers[,'p_val_adj',drop=FALSE]
colnames(genes.monkey.dp)<-'p_val'
monkey.p.genes<-DESeq_Genes(p.data = genes.monkey.dp)
```


### Anova analsis:test the important genes'mean between cell size,cell groups ,whether is equal

#### anavo analysis
```{r}
for(gene in unique(monkey.imp.lognorm.melt$variable)){
  aov.gene<-Anova.gene(data = monkey.imp.lognorm.melt,gene = gene,inter = FALSE,plot.aov = FALSE)
}
```

